---
title: "NWEA to ETO data transfer workflow"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

At the end of each trimester, CA students' NWEA scores are exported from the on-line NWEA data base into ETO. This tranfer can easily be done by following these steps:

## STEP 1: Get the data from ETO and the NWEA database
### Get the students list from ETO

To obtain this list:

1. Go to the "CA - Full Roster" homepage in ETO
1. Click on "CA REPORT: Raw Demographics"
1. At the prompt, select "CA - Full Roster" for the "Program Name" field. Leave the other fields blank.
1. Click on the "students_list" tab 
1. Save the the "students_list" report as an Excel file on your computer
1. Open it, and save it as a .csv file. __Do not skip 5, and save it directly as a .csv file, it would break the report formatting.__

### Get the students' NWEA scores from the NWEA on-line database
__To be completed__

## STEP 2: Load data into R
If you have never used the laycUtils and laycca packages before, uncomment, and run the following 2 lines of code:

```{r, eval = FALSE}

# devtools::install_github('thelayc/laycUtils', build_vignettes = TRUE)
# devtools::install_github('thelayc/laycca', build_vignettes = TRUE)
library(laycUtils)
library(laycca)
nwea <- load_csv("./path/to/nwea_scores.csv") # Edit the path to your .csv file as needed
eto <- load_csv("./path/to/students_list.csv") # Edit the path to your .csv file as needed
```

The __nwea__ dataset should have the following structure and column names:

```{r, echo = FALSE}
library(laycUtils)
library(laycca)
data(nwea_scores)
nwea <- nwea_scores
dplyr::tbl_df(nwea)
rm(nwea_scores)
```

The __eto__ dataset should have the following structure and column names:

```{r, echo = FALSE}
data(students_list)
eto <- students_list
dplyr::tbl_df(eto)
rm(students_list)
```

## STEP 3: Conduct some basic data cleaning

```{r}
nwea <- clean_nwea(nwea)
```

## STEP 4: Merge both dataset

Since the 2 datasets don't share a common ID, we will create a custom id based on students' first and last name.

```{r}
# Create custom id
nwea$custom_id <- create_id(nwea, var = c("StudentLastName", "StudentFirstName"))
eto$custom_id <- create_id(eto, var = c("lname", "fname"))
nwea$custom_id

# Merge
df <- fuzzy_join(x = nwea, y = eto, by = 'custom_id')
head(df)

```

## STEP 5: Format data for upload in ETO
```{r}
df <- format_nwea(df)
head(df)
```

## STEP 6: Save as .csv
The `export_nwea()` will automatically save the dataset in the active working directory, and name it.

```{r, eval = FALSE}
export_nwea(df)
```

## STEP 7: Save file as Excel and upload it in ETO
ETO doesn't support .csv files. It is necessary to open the newly created .csv file, and save it as an .xls file before finalizing the upload in ETO.
