---
title: "NWEA snapshot: workflow"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Before you start
Get the script template by running the following line of code:
```{r, eval=FALSE}
file.copy(from = list.files(path.package("laycca"), pattern = '\\.R$'),
          to = 'path/to/working/directory', overwrite = recursive, recursive = FALSE,
          copy.mode = TRUE)
```


## STEP 1: Get raw data from ETO
### Get the students list from ETO

To obtain this list:

1. Go to ETO: Reports > View reports
1. Run the "[LAYCCA] students_roster" report in ETO
1. At the prompt, select the date range you are interested in.
1. Click on "students_list" tab
1. Save the table as a text file (.txt extension)

### Get the students' NWEA scores from ETO

To obtain NWEA data

1. Run the "[Admin] raw_touchpoint_report_detailed"
1. At the prompt, select the date range you are interested in.
1. Save the data as a text file (.txt extension)

## STEP 2: Load data into R
If you have never used the laycUtils and laycca packages before, uncomment, and run the following 2 lines of code:

```{r, eval = FALSE}

# devtools::install_github('thelayc/laycUtils', build_vignettes = TRUE)
# devtools::install_github('thelayc/laycca', build_vignettes = TRUE)
library(laycUtils)
library(laycca)
nwea <- load_txt("./path/to/nwea_scores.txt") # Edit the path to your .csv file as needed
students <- load_txt("./path/to/students_roster.txt") # Edit the path to your .csv file as needed
```

The __nwea__ dataset should have the following structure and column names:

```{r, echo = FALSE}
library(laycUtils)
library(laycca)
data(nwea_eto)
nwea <- nwea_eto
dplyr::tbl_df(nwea)
rm(nwea_eto)
```

The __students__ dataset should have the following structure and column names:

```{r, echo = FALSE}
data(students_list)
students <- students_list
dplyr::tbl_df(students)
rm(students_list)
```
