---
title: "Career Academy Students' Progress Report"
params:
  sy: !r c('2014-2015')
  sy_end: !r lubridate::mdy('08/31/2015')
  sy_start: !r lubridate::mdy('09/01/2014')
output:
  pdf_document:
    toc: yes
  html_document:
    fig_caption: yes
    theme: readable
    toc: yes
  word_document: default
---

------

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width = 12, fig.height = 8, fig.path = 'Figs/',
                      echo = FALSE, warning = FALSE, message = FALSE, digits = 1)
```

```{r}
source('./R/utils.R')
source('./R/01_load.R')
source('./R/02_clean.R')
source('./R/03_analysis.R')
```

## NWEA administration
### Number of students who took the NWEA test for each period
`r knitr::kable(nwea_sample)`

### Number of students who took the test more than twice
`r knitr::kable(nwea_frequency)`

## Retention:
* `r enrolled` students enrolled at the Career Academy for school year 2014-15 (They had at least one NWEA score).
* `r retained` students had at least an academic pre-test and post-test
* Retention rate: `r scales::percent(retained/enrolled)`

## Students' progress
### Using NWEA scores
Out of the `r sum(df$n)` students who had matching NWEA pre / post tests, `r scales::percent(df$percent[df$change == 'positive'])` showed academic progress, as measured by the NWEA RIT Reading scale.

```{r}
cohort_progress
```

On average, students showed an increase of `r round(stat_test$estimate, 1)` on the RIT scale between their pre and post test scores.   
* `r scales::percent(attributes(stat_test$conf.int)$conf.level)` confidence interval: [`r round(stat_test$conf.int[1], 1)` ; `r round(stat_test$conf.int[2], 1)`]

```{r}
scores_distribution
```

## Appendix
This chart is not directly related to the PMF, but it gives a quick overview of students who made progress, and how much.
```{r, echo=FALSE, fig.height=14, fig.width=10}
indiv_progress
```




